\Huge{Vipassana for Hackers} \\ \large{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-09-29 paper-two/paper-two.tex
included information about the PPC and reference

The CEN is activated when high-level cognitive tasks or external goal-oriented tasks
are being performed. Executive functions are cognitive processes involved in
cognitive control of behavior. The regions of the brain involved in executive
functions are Dorsolateral Prefrontal Cortex (DL-PFC), Orbito Frontal Cortex (OFC),
and the Posterior Parietal Cortex (PPC).

@@

The DL-PFC is a part of the Prefrontal Cortex found in primates, including
humans. The DL-PFC is involved in higher cognitive processes including working memory
(holding different pieces of information, manipulating them, and using them for
tasks), selective attention, cognitive flexibility (switching between tasks) and
planning. It also seems to be involved in social cognition and lying. The DL-PFC can
increase dopamine levels in the brain. \cite{dlpfcmemory,dlpfctasks,dlpfclying}

@@

The OFC is an area found in front of both hemispheres of the brain, just above the
eye. It is again part of the Prefrontal Cortex and is thought to be involved in
decision making through emotion and reward. It also receives input from multiple
sensory modalities and in turn activates the Amygdala and the
Hypothalamus. \cite{theprefrontalcortex,ofcprimates,theorbitofrontalcortex}

\subsubsection{Posterior Parietal Cortex}

The PPC receives information from the auditory, visual and somatosensory systems and
in turn activates the Motor Cortex or DL-PFC. \cite{parietallobes}

\todo{why and how does the PCC receive external information and activate the motor cortex/DL-PFC? expand.}

@@

>>>>

The CEN is activated when high-level cognitive tasks or external goal-oriented tasks
are being performed. These tasks or executive functions are cognitive processes involved in
cognitive control of behavior. This depends on three types of brain functions : working memory,
mental flexibility and self-control. 
The regions of the brain involved in these executive functions are 
Dorsolateral Prefrontal Cortex (DL-PFC), Orbito Frontal Cortex (OFC),
and the Posterior Parietal Cortex (PPC).

@@

The DL-PFC is a part of the Prefrontal Cortex found in primates, including
humans. The DL-PFC is involved in higher cognitive processes including working memory
(holding different pieces of information, manipulating them, and using them for
tasks), selective attention, cognitive flexibility (switching between tasks) and
planning. It also seems to be involved in social cognition and lying. The DL-PFC has
also been seen to increase dopamine levels in the brain. \cite{dlpfcmemory,dlpfctasks,dlpfclying}

@@

The OFC is an area found in front of both hemispheres of the brain, just above the
eyes. It is again a part of the Prefrontal Cortex and is thought to be involved in
decision making through emotion and reward. It also receives input from multiple
sensory modalities and in turn activates the Amygdala and the
Hypothalamus. \cite{theprefrontalcortex,ofcprimates,theorbitofrontalcortex}

\subsubsection{Posterior Parietal Cortex}
The PPC is a region of the parietal cortex that is posterior to the primary somatosensory 
cortex.
The posterior parietal cortex receives input from auditory, visual, and somatosensory systems
as well as a variety of other brain regions, and it integrates this input to facilitate 
the execution of functions that require diverse information (also known as higher-order functions). 
It in turn activates the DL-PFC and motor cortex and is involved in the performance of 
attention related tasks as well as higher-order motor tasks such as grasping and catching. \cite{parietallobesa,parietallobes}

@@

\bibitem{parietallobesa}
  Caspers S, Amunts K, Zilles K. 
  \textit {Posterior Parietal Cortex: Multimodal Association Cortex.}
   The Human Nervous System. 3rd ed. New York: Elsevier; 2012.
